\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright
\pagenumbering{arabic}

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
        \begin{changemargin}{-0.05in}{-0.05in}
                \vspace*{-8pt}
                \hrulefill \\
                \vspace*{-2pt}
        \end{changemargin}
}

\newcommand{\header}[1]{
        \begin{changemargin}{-0.5in}{-0.5in}
                \scshape{#1}\\
        \lineover
        \end{changemargin}
}

\newcommand{\contact}[6]{
        \begin{changemargin}{-0.5in}{-0.5in}
                \begin{center}
                        {\Large \scshape {#1}}\\ \smallskip
                        {#2}\\ \smallskip
                        {#3}\\ \smallskip
      {#4}\\ \smallskip
                        {#5}\\ \smallskip
                        {#6}\smallskip
                \end{center}
        \end{changemargin}
}

\newenvironment{body} {
        \vspace*{-16pt}
        \begin{changemargin}{-0.25in}{-0.5in}
  }
        {\end{changemargin}
}

%-------------------------------------------------------------------------------
\begin{document}

% Name
\contact{Lakshmi Kannan}{lnkmails@gmail.com}{San Francisco Bay Area}{469-442-7891}{https://www.linkedin.com/in/kannanln}{https://www.lakshmikannan.me}

% Summary
\header{Summary}
\begin{body}
Engineering leader with experience in both seed-stage startups and web-scale companies.
Proven ability to hire and manage multi-national teams, define product roadmaps, and deliver core platform initiatives.
Experienced in building distributed systems, developer experience platforms, SaaS standardization, and site reliability engineering.
Passionate about talent, diversity, and delivering unified security and infrastructure platforms for enterprises.
\end{body}

% Experience
\header{Experience}
\begin{body}

\textbf{Vice President of Engineering}, \emph{SentinelOne} \hfill Mar 2024 -- Present \\
\begin{itemize}
  \item Lead Platform Engineering org (~260 engineers globally) across SaaS, WebApp, Developer Experience, Cloud Infra, and SRE.
  \item Drove standardization across SaaS products (SSO, licensing, usage/metering, lifecycle management).
  \item Built unified design systems across web apps, improved developer efficiency (CI/CD pipelines, multi-cloud infra across AWS, GCP, FedRamp).
  \item Oversaw reliability of all SaaS products powering SentinelOne Unity platform (endpoint, XDR, identity, threat services).
\end{itemize}

\textbf{Senior Director of Engineering}, \emph{SentinelOne} \hfill Aug 2021 -- May 2024 \\
\begin{itemize}
  \item Directed teams delivering Security Data Lake (core of Singularity Unity Vision).
  \item Recruited and scaled 40+ ICs and managers across multiple geos.
  \item Managed both product software (UI, microservices, infra) and SRE/ops teams supporting \$700M+ ARR business.
\end{itemize}

\textbf{Director of Engineering}, \emph{SentinelOne} \hfill Feb 2021 -- Aug 2021 \\
\begin{itemize}
  \item Oversaw Scalyr integration post-acquisition and SentinelOne IPO.
  \item Migrated Scalyr services to Kubernetes, modernized deployment across regions, and transitioned IT/compliance/ops to SentinelOne standards.
  \item Optimized infrastructure costs (migrated ELK stack to Scalyr).
\end{itemize}

\textbf{Director of Engineering}, \emph{Scalyr} \hfill Oct 2019 -- Mar 2021 \\
\begin{itemize}
  \item Led Cloud Tech and SRE teams; owned open-source agent, ingestion pipelines, and compliance/security.
  \item Implemented SLO/error budgets, incident response program, and automation-focused operations.
  \item Temporarily led Customer Success; directly interfaced with customers.
\end{itemize}

\textbf{Director, Software Engineering}, \emph{Extreme Networks} \hfill Oct 2017 -- Oct 2019 \\
\begin{itemize}
  \item Drove SaaS strategy; led transition from on-prem to cloud products including Network Management and Workflow Automation SaaS.
  \item Helped open new office in Shannon, Ireland with IDA funding; hired first managers and engineers.
\end{itemize}

\textbf{Software Manager}, \emph{Brocade (via StackStorm acquisition)} \hfill Mar 2016 -- Oct 2017 \\
\begin{itemize}
  \item Shipped Brocade Workflow Composer, enabling enterprises to automate both cloud and network operations.
  \item Managed 10 engineers globally; delivered 5 major releases in 1 year through 2 acquisitions.
\end{itemize}

\textbf{Staff Engineer \& Tech Lead}, \emph{StackStorm} \hfill Jun 2014 -- Mar 2016 \\
\begin{itemize}
  \item Early engineer; built auto-remediation platform, designed key components, and led engineering team.
  \item Supported open-source release (st2) and built strong community presence.
\end{itemize}

\textbf{Sr. Software Development Engineer}, \emph{Rackspace} \hfill Jun 2012 -- May 2014 \\
\begin{itemize}
  \item Built cloud monitoring and metrics platform (Blueflood) later open-sourced.
  \item Scaled product from internal SaaS component to independent cloud service.
\end{itemize}

\textbf{Software Development Engineer}, \emph{Amazon} \hfill May 2010 -- May 2012 \\
\begin{itemize}
  \item Designed archival and repartitioning systems for cloud storage, ensuring live migrations without downtime.
  \item Gained strong operational experience in large-scale distributed systems.
\end{itemize}

\textbf{Research Assistant}, \emph{University of Texas at Dallas} \hfill Oct 2005 -- Dec 2009 \\
\begin{itemize}
  \item Researched cooperative wireless protocols and stochastic modeling at OpNeAR Lab.
\end{itemize}

\textbf{Internships} \hfill 2009 \\
\begin{itemize}
  \item Biscotti Inc.: Built wireless emulator based on NIST Net. (C, 802.11 MAC)
  \item Iridescent Networks: Developed RTSP media proxy. (C, C++, RTSP, SIP)
\end{itemize}

\end{body}

% Education
\header{Education}
\begin{body}
\textbf{The University of Texas at Dallas} \hfill 2005 -- 2010 \\
Ph.D., Electrical Engineering
\end{body}

% Skills
\header{Skills}
\begin{body}
\begin{itemize}
  \item Distributed Systems, Cloud Platforms, SaaS Engineering, SRE/DevOps
  \item Python, C++, Java, C, JavaScript (plus exposure to Go, Rust, Scala)
  \item Product \& Platform Strategy, Multi-national Hiring, Incident Management, Compliance (SOC2)
\end{itemize}
\end{body}

% Certifications
\header{Certifications}
\begin{body}
\begin{itemize}
  \item Business Essentials
\end{itemize}
\end{body}

\end{document}
